---
title: "hw3_1"
author: "Nikita Kartashov"
date: "24 April 2015"
output: html_document
---

```{r}
library(MASS)
```


```{r}
df <- read.table("../data/1.txt")
columns.for.fitting <- c("body.fat", 'age', 'weight', 'height', 'BMI', 'neck', 'chest', 'abdomen', 'hip', 'thigh', 'knee', 'ankle', 'bicep', 'forearm', 'wrist')
df <- df[, columns.for.fitting]
names(df)[names(df)=="body.fat"] <- "Y"
model <- lm(Y ~ ., data=df)
summary(model)
reduced.model <- stepAIC(model)
summary(reduced.model)
```

Determination coefficient for the reduced model is 0.7467.
But let's plot all the data and try to stare at it really hard (also, diagnostics).

```{r}
library(knitr)
library(lattice)
library(e1071)
library(corrplot)
library(latticeExtra)
```

```{r}
plotVariable <- function(param) {
  formula <- reformulate(termlabels = param, response = 'Y')
  xyplot(formula, panel=function(...) {  
  panel.xyplot(...)
  panel.loess(...)
  }, data = df, xlab = param, ylab = "Y")
}

plotVariables <- function() {
  for (i in colnames(df)[-1]) {
    print(plotVariable(i)) 
  }
}
```

```{r}
plotVariables()
```

```{r}
plot(reduced.model)
```

We cannot help but notice an outlier to the right on plots ankle (although ankle has many outliers), abdomen, weight, BMI, neck, chest, hip, thigh, knee, whose measurements are high while body fat is relatively low, number 39, it's also has a very hight leverage, let's remove him and fit again.

```{r}
df <- df[-c(39), ]
```

```{r}
model <- lm(Y ~ . , data=df)
summary(model)
reduced.model <- stepAIC(model, direction = "backward")
summary(reduced.model)
```

Looks like RSE improved.